Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-04-24 paper.tex
fixed brackets

A \ac{DecPOMDP} represents a sequential game, 
 in which each agent receives a local observation about the world they 
 inhabit and receives a joint immediate reward in response to the actions they take. 
% 
\ga{Improve, if necessary, the following paragraph.}
Formally, a DecPOMDP is defined as a tuple $<N, S, \{A_i\}, P, R, \{\Omega_i\}, O, \gamma>$, 
 where $N$ is the total number of agents that live in the environment, 
 $S$ is the state set of the environment, 
 $\{A_i\}$ is the set of actions for agent $i$ and $A$ is the joint action space, 
 $P$ is the probability transition function, 
 $R$ is the immediate joint reward function, and 
 $\{\Omega_i\}$ is the set observation function for the agent $i$,
 $O$ is the observation space, and finally $\gamma$ is the discount factor.
%
On top of this model, each agent try to learn a policy $\pi_i$ in order 
 to maximise the long term join reward signal.

>>>>

A \ac{DecPOMDP} represents a sequential game, 
 in which each agent receives a local observation about the world they 
 inhabit and receives a joint immediate reward in response to the actions they take. 
% 
\ga{Improve, if necessary, the following paragraph.}
Formally, a DecPOMDP is defined as a tuple $\langle N, S, \{A_i\}, P, R, \{\Omega_i\}, O, \gamma \rangle$, 
 where $N$ is the total number of agents that live in the environment, 
 $S$ is the state set of the environment, 
 $\{A_i\}$ is the set of actions for agent $i$ and $A$ is the joint action space, 
 $P$ is the probability transition function, 
 $R$ is the immediate joint reward function, and 
 $\{\Omega_i\}$ is the set observation function for the agent $i$,
 $O$ is the observation space, and finally $\gamma$ is the discount factor.
%
On top of this model, each agent try to learn a policy $\pi_i$ in order 
 to maximise the long term join reward signal.
